\includegraphics*[width=0.4\textwidth]{hpi_logo_2017.eps}\\ \vspace{24pt} Genetic Doodle Jump

### 2018-03-31 paper/paper.tex
more related work

\usepackage{color}

@@

In the paragraph we present some related work. In the following two sections, we introduce the basics of the Doodle Jump game in detail and give a rough overview of our user interface. After that, we pay special attention to the used neural network. In section \ref{sec:ga} we present our genetic algorithm, in particular with focus on the basic operations of this algorithm and its evaluation. Finally, we conclude our work and show some interesting findings.

@@

There can be a broad range of bots playing different games on the internet. We could compare our approach with their work, which does not make sense when it comes to comparing the results. For this reason, we use a similar implementation for comparison. 
TODO describe this: https://github.com/eshohet/doodle-jump-machine-learning

@@

Since we do not want to perform the deep learning part on a mobile device or within an emulator, we decided to use an implementation, which runs in a browser. We are using \quot{HTML5 Doodle Jump} by ntcnet83\footnote{\url{https://github.com/ntcnet83/html5-doodle-jump}}, which we found on github\footnote{\url{https://github.com/}}. This custom version of the is written in HTML5 and JavaScript. The doodler can be control via left and right arrow keys. In contrast to the original implementation, this version of the game contains less features, which makes the game simpler at the end:
\begin{itemize}
\item Except springs, there are no other bonuses.
\item There are no enemies. Hence, the only way to die is falling down.
\item The feature shooting is not necessary and therefore not available.
\item The game does not have vertically moving platforms.
\item The difficulty changes after a certain score, but only through the usage of more moving and vanishable platforms. The distances between the platforms stay the same.
\end{itemize}

>>>>

\usepackage{color}
% \usepackage{subfig}

@@

In the next paragraph we present some related work. In the following two sections, we introduce the basics of the Doodle Jump game in detail and give a rough overview of our user interface. After that, we pay special attention to the used neural network. In section \ref{sec:ga} we present our genetic algorithm, in particular with focus on the basic operations of this algorithm and its evaluation. Finally, we conclude our work and show some interesting findings.

@@

A broad range of bots playing different games can be found on the internet. We could compare our approach with their work, which does not make sense in terms of comparing the results. For this reason, we use a similar implementation for comparison. The approach of \textit{Shohet et al.}\cite{eshohet} uses reinforcement learning for playing Doodle Jump. The game's implementation they use is exactly the same as we use.

Shohet uses a Q-Learning algorithm, which is model-free. This technique depends on states. Depending on the current state an action will be calculated in order to go into the next state. Based on the impact of the action a reward will be awarded. If this action has a negative effect, for example the player falls down and dies, the evaluation is bad. Otherwise, the it will be positive. Based on those rewards, the algorithm learns when to use which actions in order to become better.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/performance_others}
  \caption{Performance of reinforcement learning\cite{eshohet}}
  \label{fig:perf_other}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/performance_others}
  \caption{\color{red}{TODO insert our image}}
  \label{fig:our_perf}
\end{subfigure}
\end{figure}

@@

Since we do not want to perform the deep learning part on a mobile device or within an emulator, we decided to use an implementation, which runs in a browser. We are using \quot{HTML5 Doodle Jump} by Cong Nguyen\footnote{\url{https://github.com/ntcnet83/html5-doodle-jump}}, which we found on github\footnote{\url{https://github.com/}}. This custom version of the is written in HTML5 and JavaScript. The doodler can be control via left and right arrow keys. In contrast to the original implementation, this version of the game contains less features, which makes the game simpler at the end:
\begin{itemize}
\item Except springs, there are no other bonuses.
\item There are no enemies. Hence, the only way to die is falling down.
\item The feature shooting is not necessary and therefore not available.
\item The game does not have vertically moving platforms.
\item The difficulty changes after a certain score, but only through the usage of more moving and vanishable platforms. The distances between the platforms stay the same.
\end{itemize}
